---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SticsPubRTools

<!-- badges: start -->
<!-- badges: end -->

The goal of SticsPubRTools is to ...

## Prerequisites and technical tips


## Installation


The package installation can be done directly from [GitHub](https://github.com/) using either `devtools` or the lightweight one [remotes](https://github.com/r-lib/remotes#readme) package

The last release version can be installed using:

* With `devtools`

``` r
devtools::install_github("SticsRPacks/SticsPubRTools@*release")
```
* With `remotes`

``` r
# install.packages("remotes")
remotes::install_github("SticsRPacks/SticsPubRTools@*release")
```

Or the current development version can be installed using:
``` r
devtools::install_github("SticsRPacks/SticsPubRTools")
```


Normaly, all the package dependencies will be installed for CRAN packages.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SticsPubRTools)
## basic example code
```


